\LARGE \bf Exploiting Non-Slip Wall Contacts \\ to Position Two Particles Using The Same Control Input

### 2018-12-07 journalWallFriction/theory2robAlgs.tex
fixed figure 3  (whew!)

The  $\Delta$ configuration space for an $n$-sided convex polygon $P$ can be constructed in a method analogous to computing configuration space obstacles for polygons~\cite{lozano1983spatial}. 
 Translate $n$ copies of $P$  so that each copy moves a different vertex of $P$ to $(0,0)$.
Because $P$ is convex, the convex-hull of all these translated vertices is the boundary of the  $\Delta$ configuration space.
 For an $n$-sided convex polygon, the $\Delta$ configuration space is a $2n$-sided convex polygon.
  Even-sided regular polygons are a special case in which half the sides align and the $\Delta$ configuration space is $n$-sided. 
An example $\Delta$ configuration space construction is shown in Fig.~\ref{fig:irregular}: 
a four-sided workspace is on the left, 
the four translated copies with dashed lines outlining the convex hull is in the middle,
 and the resulting $\Delta$ configuration space is on the right.  
% The 2-move reachable sets for the given $\Delta$s starting configuration are drawn in transparent blue.
%The following subsection describes how 2-move reachable sets are constructed.
\begin{figure}
\centering
\begin{overpic}[width=\columnwidth]{irregular.pdf}
\put(0,10){\scriptsize
$\Delta s$ \tikz \draw[green,fill=green,line width=0.3mm] (-1ex,0) rectangle (0,1ex); $=$
\tikz \draw[red,fill=red,line width=0.3mm] (-1ex,0) rectangle (0,1ex); $-$
\tikz \draw[blue,fill=blue,line width=0.3mm] (-1ex,0) rectangle (0,1ex); 
}
\put(0,5){\scriptsize
$\Delta g$ \tikz \draw[green,fill=green,line width=0.3mm] (0,0) circle (0.5ex); $=$
\tikz \draw[red,fill=red,line width=0.3mm] (0,0) circle (0.5ex); $-$
\tikz \draw[blue,fill=blue,line width=0.3mm] (0,0) circle (0.5ex); 
}
\end{overpic}
\caption{\label{fig:irregular}
Workspace and $\Delta$ configuration space is shown for an arbitrary convex polygon with $n=4$ sides. The 2-move reachable sets for this initial configuration ($\Delta s= s_2-  s_1$) are drawn in transparent blue.}
\end{figure}

>>>>

The  $\Delta$ configuration space for an $n$-sided convex polygon $P$ can be constructed in a method analogous to computing configuration space obstacles for polygons~\cite{lozano1983spatial}. 
 Translate $n$ copies of $P$  so that each copy moves a different vertex of $P$ to $(0,0)$.
Because $P$ is convex, the convex-hull of all these translated vertices is the boundary of the  $\Delta$ configuration space.
 For an $n$-sided convex polygon, the $\Delta$ configuration space is a $2n$-sided convex polygon.
  Even-sided regular polygons are a special case in which half the sides align and the $\Delta$ configuration space is $n$-sided. 
An example $\Delta$ configuration space construction is shown in Fig.~\ref{fig:irregular}: 
a four-sided workspace is on the left, 
the four translated copies with dashed lines outlining the convex hull is in the middle,
 and the resulting $\Delta$ configuration space is on the right.  
% The 2-move reachable sets for the given $\Delta$s starting configuration are drawn in transparent blue.
%The following subsection describes how 2-move reachable sets are constructed.
\begin{figure}
\centering
\begin{overpic}[width=\columnwidth]{irregular.pdf}
%\put(0,10){\scriptsize
%$\Delta s$ \tikz \draw[green,fill=green,line width=0.3mm] (-1ex,0) rectangle (0,1ex); $=$
%\tikz \draw[red,fill=red,line width=0.3mm] (-1ex,0) rectangle (0,1ex); $-$
%\tikz \draw[blue,fill=blue,line width=0.3mm] (-1ex,0) rectangle (0,1ex); 
%}
%\put(0,5){\scriptsize
%$\Delta g$ \tikz \draw[green,fill=green,line width=0.3mm] (0,0) circle (0.5ex); $=$
%\tikz \draw[red,fill=red,line width=0.3mm] (0,0) circle (0.5ex); $-$
%\tikz \draw[blue,fill=blue,line width=0.3mm] (0,0) circle (0.5ex); 
%}
\end{overpic}
\caption{\label{fig:irregular}
Workspace and $\Delta$ configuration space is shown for an arbitrary convex polygon with $n=4$ sides.
% The 2-move reachable sets for this initial configuration ($\Delta s= s_2-  s_1$) are drawn in transparent blue.
}
\end{figure}
